Sentiment Analysis of Twitter in Relation to Fossil Fuel Stock Prices

### 2023-04-21 manuscript/manuscript.tex
quick comments

\title{Sentiment Analysis of Twitter in Relation to Fossil Fuel Stock Prices}
\author{Pranav Tavildar\\
  University of Connecticut
}

@@

\bigskip
\noindent{\sc Keywords}:
BERT;
chevron;
twitter;
nlp;
sentiment analysis.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec: intro}
%\paragraph{Overview of topic}
\paragraph{}

@@

	\paragraph{}
	As a publicly traded company, Chevron's stock price is determined by supply and demand in the market. Generally, this is influenced by factors such as market dynamics, economic conditions and changes to economic policy. Through this paper, we seek to determine whether this can be predicted or determined through observing public speculation on Twitter, the "virtual public square." Being able to determine whether public sentiment can be informative in predicting stock price might prove as a valuable indicator for many groups such as investors, activists, and companies officials to determine how much of a correlation a change in public opinion has to the stock value.  	
%\paragraph{Review of the Literature}
\paragraph{}

@@

\paragraph{}
	 Some papers in the literature use this technique in relation to analyzing activity in the stock market. Koosha Golmohammadi and Osmar R. Zaiane for instance use sentiment analysis with Twitter data to improve their Contextual Anomaly Detection(CAD) model in order to detect Market Manipulation in the United States and Canada \citep{golmohammadi2017sentiment}. Furthermore, Lu-Tao Zhao and Guan-Rong Zheng web text and applied Sentiment Analysis in order to do Oil Price forecasting \citep{zhao2019forecasting}. This concept has also been applied in order to predict one step ahead of the closing price of the stock market in Thailand using a hybrid model composed of Principle Component Analysis (PCA) for Data Processing (Dimensionality Reduction), Empirical Mode Distribution (EMD) for signal interpretation and data preprocessing, and the Long-Short-Term-Memory(LSTM) model, a specialized type of recurrent neural network for the sentiment analysis. \citep{srijiranon2022hybrid}
\paragraph{}

@@

\paragraph{}
	This model sought to improve the problems existing with the Recurrent Neural Network(RNN) model which used to be the preferred model for language processing tasks. Transformers have shown a lot of promise, outperforming its competitors in speed and accuracy for natural language processing tasks. Due to its novelty and its promising qualities, many are applying Transformers for various tasks, yet nobody has this used this approach to find out whether it is possible to find out the correlation between Twitter Sentiment and Stock prices of prominent fossil fuel corporations. In this paper, we specifically will focus on the Chevron Corporation (though in future iterations, we might extend this to multiple corporations in this field).
%\paragraph{My Contribution}
\paragraph{}

@@

\paragraph{}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\label{sec: datadesc}
\section{Data Description}
\paragraph{}
	For the period of 2021-2022,  CVX stock data and twitter tweets were collected for analysis.
%%\paragraph{how the economic data was obtained}
\paragraph{}
	Historic Stock data for the Chevron Corporation was collected using Yahoo Finance's Historical Stock Data tool. The following is a figure that shows the fluctuations of the Stock Highs, the Stock Lows and the Closing Prices over the observed period that was generated using the matplotlib package for python \citep{Hunter_2007}.

@@

\paragraph{}
	While the Highs and Lows might be informative in analysis, in order to concentrate the focus of this paper in a manner more similar to other financial data analyses, we will only experiment the Closing Price and the Returns which can be taken by taking the log difference of the Closing Prices.

\begin{figure}[!hb]
  \begin{center}
  \includegraphics[width=\textwidth]{../figures/fig2.pdf}
  \caption{A plot of historic CVX stock data from 2021 to 2022 and the returns}\label{fig:fig2}
  \end{center}
\end{figure}

\paragraph{}
	We also used the data processing library Pandas in order to generate summary statistics as shown below:
\begin{table}[!hb]
  \begin{center}
    \caption{Summary Statistics for the Chevron Stock data}
    \label{tab:table1}
    \begin{tabular}{l|c|r} % <-- Alignments: 1st column left, 2nd middle and 3rd right, with vertical lines in between
      \textbf{Metrics} & \textbf{Close} & \textbf{Returns}\\
      \hline
      count & 503.000000 & 502.000000\\
      mean & 131.520815 & 0.001496\\
      std & 30.228298 & 0.018412\\
      min & 84.709999	 & - 0.069374\\
      25\% & 103.989998 & -0.008429\\
      50\% & 118.790001 & 0.002891\\
      75\% & 160.619995 & 0.013058\\
      max & 188.050003 & 0.085292\\
    \end{tabular}
  \end{center}
\end{table}

\paragraph{}
	The range of the closing values for the observed period was 84.70 to 188.05; the lowest and highest values were observed on January 4th, 2021 November 15th, 2022. There are 502 days that the stock data was available for since Chevron is a part of the New York Stock Exchange which is closed all day on Saturdays, Sundays and nine holidays a year. This was something that was taken into consideration when working with twitter data.

\paragraph{}
	The twitter data was scraped using the python package snscrape \citep{justanotherarchivist_2022}. This is an open source library that allows for the scraping of twitter data without having to use the API. The code used to generate the twitter data can be found in code/datagen.py. In short, the process used to scrape the data was to first create some auxiliary functions for tasks such as determining how many tweets need to be gathered at a given time and create some functions to make it easier to pass in queries in the Twitter Search Scraper object. Regarding the collection of tweets, the query can either be for some topic keywords or the tweets from a specific user.

\paragraph{}
	For the purpose of this paper, 10 tweets were scraped with the topic query "CVX" from January 1st 2021 to December 31st 2022.  7290 tweets were generated, saved as a csv and merged with the CVX stock data on the Date axis after matching datatypes. This also omitted tweets which were created when the stock market was closed in order to simplify the analysis. Using this we were able to perform sentiment analysis and calculate correlation.

@@

\begin{figure}[H]
\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt        
\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
%Rounded Rect [id:dp4434986972980839] 
\draw   (100,43.8) .. controls (100,32.76) and (108.95,23.8) .. (120,23.8) -- (261,23.8) .. controls (272.05,23.8) and (281,32.76) .. (281,43.8) -- (281,103.8) .. controls (281,114.85) and (272.05,123.8) .. (261,123.8) -- (120,123.8) .. controls (108.95,123.8) and (100,114.85) .. (100,103.8) -- cycle ;
%Rounded Rect [id:dp8739677930569794] 
\draw   (359,68.2) .. controls (359,52.52) and (371.72,39.8) .. (387.4,39.8) -- (472.6,39.8) .. controls (488.28,39.8) and (501,52.52) .. (501,68.2) -- (501,168.4) .. controls (501,184.09) and (488.28,196.8) .. (472.6,196.8) -- (387.4,196.8) .. controls (371.72,196.8) and (359,184.09) .. (359,168.4) -- cycle ;
%Curve Lines [id:da9359490056283244] 
\draw    (282,73) .. controls (362,56.8) and (275,143.8) .. (359,124.8) ;
%Straight Lines [id:da03881732608220867] 
\draw    (78,72.8) -- (101,73) ;
%Straight Lines [id:da6091063106538472] 
\draw    (500,120.8) -- (523,121) ;
%Straight Lines [id:da19347919375178857] 
\draw    (431,215.8) -- (431,199.8) ;
% Text Node
\draw (161,65) node [anchor=north west][inner sep=0.75pt]   [align=left] {Encoder};
% Text Node
\draw (398,103) node [anchor=north west][inner sep=0.75pt]   [align=left] {Decoder};
% Text Node
\draw (42,63) node [anchor=north west][inner sep=0.75pt]   [align=left] {Input};
% Text Node
\draw (524,112) node [anchor=north west][inner sep=0.75pt]   [align=left] {Output};
% Text Node
\draw (408,219) node [anchor=north west][inner sep=0.75pt]   [align=left] { Output Probabilites};
\end{tikzpicture}
\caption{In this figure we can observe a very simplified version of the Transformer model with its two major components, the encoder and the decoder.\citep{devlin2018bert}}\label{fig:fig2}
\end{figure}
The Transformer architecture consists of two main components: an encoder and a decoder.The encoder takes in the input sequence and generates a sequence of hidden representations, which are then passed to the decoder. The decoder then uses the encoder's output to generate the final output sequence.

\paragraph{}
We will be utilizing Bidirectional Encoder Representations from Transformers (BERT) for our sentiment analysis. BERT is a transformer model developed by Google that can perform multiple Natural Language Processing tasks such as sentiment analysis, text classification, chatbots, text extraction, machine translation, text summarization, market intelligence, auto-correct, intent classification, urgency detection, and speech recognition.

\paragraph{}
This model was initially trained on Wikipedia and Google’s BooksCorpus which contain 2,500,000,000 words and 800,000,000 words respectively. Training of BERT was completed over a period of 4 days using 64 Tensor Processing Units running in parallel. With this much data, it is able to understand context clues making it a very effective model for the purposes of sentiment analysis.

\paragraph{}
We will be specifically using distil-BERT which is a version of BERT with 12 transformation layers, and 768 Hidden Layers.\citep{muller_2022} This is more reasonable for the task we have at hand and we will implement this using the Hugging Face transformers pipeline package\citep{huggingface2023}. For each day, the average sentiment score of all tweets was calculated. Sentiment scores range from -1 to 1, where -1 represents a very negative sentiment and 1 represents a very positive sentiment.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\label{sec: results}
\section{Results}
\paragraph{}
The sentiment analysis took approximately 12 minutes to run and the data generated created 3 new columns in the working dataframe: sentiment, label, and score. Score is a numeric value from the range [0,1] where the higher the score the more confident the sentiment analyzed is correct. This score is the confidence that the model gives for the sentiment assignment and serves as a way to observe sentiment as a continuous variable. When combined and observed as a frequency histogram, it seems that the sentiment scores for the period are centered around a slightly positive value of 0.1 indicating sentiment for the CVX term was generally positive but normally distributed more or less.

\begin{figure}[H]
  \begin{center}
  \includegraphics[width=\textwidth]{../figures/fig3.pdf}
  \caption{Sentiment Distribution }\label{fig:fig2}
  \end{center}
\end{figure}

\paragraph{}
ARMA-GARCH models have several assumptions, including the stationarity of the time series data, the presence of autoregressive and moving average processes, the normality and lack of autocorrelation in the residuals, the constant conditional variance of the data, the absence of autoregressive conditional heteroscedasticity effects, and a sufficient sample size. These assumptions are important to ensure unbiased parameter estimates and accurate predictions. Some of these assumptions such as the normality and lack of autocorrelation in the residuals, the constant conditional variance of the data, the absence of autoregressive conditional heteroscedasticity effects were checked manually by making plots using R as such:
\begin{figure}[!hb]
  \begin{center}
  \includegraphics[width=\textwidth]{../figures/fig4.pdf}
  \caption{Garch Model Residuals}\label{fig:fig1}
  \end{center}
\end{figure}

 and those that remained were checked by the rugarch\citep{rugarch}, readr\citep{readr}, forecast\citep{forecast}, tseries\citep{tseries}, garchx\citep{garchx}, and TSA\citep{TSA} packages.

\paragraph{}
In the analysis, an ARMA-GARCH model was first created only using the daily sentiment and then comparing to an ARMA-GARCH model with daily sentiment as an exogenous variable. The ARMA part of this technique, models the autocorrelation and moving average patterns in the data and GARCH models the volatility or conditional heteroskedasticity of the data. To determine whether daily sentiment, the exogenous variable has any effect on the model, we conducted the Likelihood ratio test. The log likelihood values for the base model and the model with sentiment as a variable are 1293.56 and 504.85, respectively.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\label{sec: discussion}
\section{Discussion}
\paragraph{}
	As mentioned before, this paper is the first one to take the approach of using Transformers to determine whether twitter sentiment is informative in predicting the volatility of the stock price of the Chevron Corporation. In summary, this paper accomplished this task through the following:
\begin{itemize}
    \item Introducing some background behind the Chevron Corporation and Sentiment Analysis as a Practice.
    \item Describing the data and the methods by which the data was obtained.
    \item Describing the methods behind the sentiment analysis and correlation derivation
    \item Describing the results

\end{itemize}
\paragraph{Possible Expansions}
	One possible expansion of this study would be to increase the sample size to include more observations and thus increase the robustness of the analysis. This would allow for more accurate statistical tests and a better understanding of the relationship between sentiment and stock price movement/volatility. Another possible expansion would be to test for causality using techniques like the Granger causality test, which would allow us to determine whether sentiment scores are truly predictive of stock price movements or whether they are just correlated. Additionally, conducting a meta-analysis of multiple companies in the fossil fuel industry or across multiple industries could provide broader insights into the relationship between sentiment and stock prices.

@@

\paragraph{Conclusion}
Overall, this study provides valuable insights into the use of Twitter sentiment analysis as a tool for predicting stock prices, and points towards potential avenues for further research. With further research, determined but analyzing the effect of public sentiment on stock prices of fossil fuel companies can provide valuable insight into how public opinion can be used to augment or reduce the effects of climate change.
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bigskip
\bibliographystyle{chicago}
\bibliography{references}

>>>>

\title{Sentiment Analysis of Twitter in Relation to Fossil Fuel Stock Prices}
\author{Pranav Tavildar\\
  University of Connecticut \\
  Advisor: Jun Yan\\
  Department of Statistics\\
  University of Connecticut
}

@@

\jy{alphabetical; no repeating words in title. Read my writing tips and practice them}
\bigskip
\noindent{\sc Keywords}:
BERT;
chevron;
twitter;
nlp;
sentiment analysis.

@@

\jy{what do I recommend for linewidth?}

\jy{Two figure labels are multiply defined. Read the log and fix the warnings}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec: intro}
%\paragraph{Overview of topic}

@@

As a publicly traded company, Chevron's stock price is determined by supply and demand in the market. Generally, this is influenced by factors such as market dynamics, economic conditions and changes to economic policy. Through this paper, we seek to determine whether this can be predicted or determined through observing public speculation on Twitter, the "virtual public square." Being able to determine whether public sentiment can be informative in predicting stock price might prove as a valuable indicator for many groups such as investors, activists, and companies officials to determine how much of a correlation a change in public opinion has to the stock value.  	
%\paragraph{Review of the Literature}

@@

 Some papers in the literature use this technique in relation to analyzing activity in the stock market. Koosha Golmohammadi and Osmar R. Zaiane for instance use sentiment analysis with Twitter data to improve their Contextual Anomaly Detection(CAD) model in order to detect Market Manipulation in the United States and Canada \citep{golmohammadi2017sentiment}. Furthermore, Lu-Tao Zhao and Guan-Rong Zheng web text and applied Sentiment Analysis in order to do Oil Price forecasting \citep{zhao2019forecasting}. This concept has also been applied in order to predict one step ahead of the closing price of the stock market in Thailand using a hybrid model composed of Principle Component Analysis (PCA) for Data Processing (Dimensionality Reduction), Empirical Mode Distribution (EMD) for signal interpretation and data preprocessing, and the Long-Short-Term-Memory(LSTM) model, a specialized type of recurrent neural network for the sentiment analysis \citep{srijiranon2022hybrid}.

@@

This model sought to improve the problems existing with the Recurrent Neural Network(RNN) model which used to be the preferred model for language processing tasks. Transformers have shown a lot of promise, outperforming its competitors in speed and accuracy for natural language processing tasks. Due to its novelty and its promising qualities, many are applying Transformers for various tasks, yet nobody has this used this approach to find out whether it is possible to find out the correlation between Twitter Sentiment and Stock prices of prominent fossil fuel corporations. In this paper, we specifically will focus on the Chevron Corporation (though in future iterations, we might extend this to multiple corporations in this field).
%\paragraph{My Contribution}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\label{sec: datadesc}
\section{Data Description}

For the period of 2021-2022,  CVX stock data and twitter tweets were collected for analysis.
%%\paragraph{how the economic data was obtained}

Historic Stock data for the Chevron Corporation was collected using Yahoo Finance's Historical Stock Data tool. The following is a figure that shows the fluctuations of the Stock Highs, the Stock Lows and the Closing Prices over the observed period that was generated using the matplotlib package for python \citep{Hunter_2007}.

\jy{the figure x-labels are cutoff}

@@

While the Highs and Lows might be informative in analysis, in order to concentrate the focus of this paper in a manner more similar to other financial data analyses, we will only experiment the Closing Price and the Returns which can be taken by taking the log difference of the Closing Prices.

\jy{The upper panel is repeating. Only keep one.}
\begin{figure}[!hb]
  \begin{center}
  \includegraphics[width=\textwidth]{../figures/fig2.pdf}
  \caption{A plot of historic CVX stock data from 2021 to 2022 and the returns}\label{fig:fig2}
  \end{center}
\end{figure}

\jy{Use table styles from my template}
We also used the data processing library Pandas in order to generate summary statistics as shown below:
\begin{table}[!hb]
  \begin{center}
    \caption{Summary Statistics for the Chevron Stock data}
    \label{tab:table1}
    \begin{tabular}{l|c|r} % <-- Alignments: 1st column left, 2nd middle and 3rd right, with vertical lines in between
      \textbf{Metrics} & \textbf{Close} & \textbf{Returns}\\
      \hline
      count & 503.000000 & 502.000000\\
      mean & 131.520815 & 0.001496\\
      std & 30.228298 & 0.018412\\
      min & 84.709999	 & - 0.069374\\
      25\% & 103.989998 & -0.008429\\
      50\% & 118.790001 & 0.002891\\
      75\% & 160.619995 & 0.013058\\
      max & 188.050003 & 0.085292\\
    \end{tabular}
  \end{center}
\end{table}

The range of the closing values for the observed period was 84.70 to 188.05; the lowest and highest values were observed on January 4th, 2021 November 15th, 2022. There are 502 days that the stock data was available for since Chevron is a part of the New York Stock Exchange which is closed all day on Saturdays, Sundays and nine holidays a year. This was something that was taken into consideration when working with twitter data.

The twitter data was scraped using the python package snscrape \citep{justanotherarchivist_2022}. This is an open source library that allows for the scraping of twitter data without having to use the API. The code used to generate the twitter data can be found in code/datagen.py. In short, the process used to scrape the data was to first create some auxiliary functions for tasks such as determining how many tweets need to be gathered at a given time and create some functions to make it easier to pass in queries in the Twitter Search Scraper object. Regarding the collection of tweets, the query can either be for some topic keywords or the tweets from a specific user.

For the purpose of this paper, 10 tweets were scraped with the topic query "CVX" from January 1st 2021 to December 31st 2022.  7290 tweets were generated, saved as a csv and merged with the CVX stock data on the Date axis after matching datatypes. This also omitted tweets which were created when the stock market was closed in order to simplify the analysis. Using this we were able to perform sentiment analysis and calculate correlation.

@@

\begin{figure}[tbp]
\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt        
\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300
%Rounded Rect [id:dp4434986972980839] 
\draw   (100,43.8) .. controls (100,32.76) and (108.95,23.8) .. (120,23.8) -- (261,23.8) .. controls (272.05,23.8) and (281,32.76) .. (281,43.8) -- (281,103.8) .. controls (281,114.85) and (272.05,123.8) .. (261,123.8) -- (120,123.8) .. controls (108.95,123.8) and (100,114.85) .. (100,103.8) -- cycle ;
%Rounded Rect [id:dp8739677930569794] 
\draw   (359,68.2) .. controls (359,52.52) and (371.72,39.8) .. (387.4,39.8) -- (472.6,39.8) .. controls (488.28,39.8) and (501,52.52) .. (501,68.2) -- (501,168.4) .. controls (501,184.09) and (488.28,196.8) .. (472.6,196.8) -- (387.4,196.8) .. controls (371.72,196.8) and (359,184.09) .. (359,168.4) -- cycle ;
%Curve Lines [id:da9359490056283244] 
\draw    (282,73) .. controls (362,56.8) and (275,143.8) .. (359,124.8) ;
%Straight Lines [id:da03881732608220867] 
\draw    (78,72.8) -- (101,73) ;
%Straight Lines [id:da6091063106538472] 
\draw    (500,120.8) -- (523,121) ;
%Straight Lines [id:da19347919375178857] 
\draw    (431,215.8) -- (431,199.8) ;
% Text Node
\draw (161,65) node [anchor=north west][inner sep=0.75pt]   [align=left] {Encoder};
% Text Node
\draw (398,103) node [anchor=north west][inner sep=0.75pt]   [align=left] {Decoder};
% Text Node
\draw (42,63) node [anchor=north west][inner sep=0.75pt]   [align=left] {Input};
% Text Node
\draw (524,112) node [anchor=north west][inner sep=0.75pt]   [align=left] {Output};
% Text Node
\draw (408,219) node [anchor=north west][inner sep=0.75pt]   [align=left] { Output Probabilites};
\end{tikzpicture}
\caption{In this figure we can observe a very simplified version of the Transformer model with its two major components, the encoder and the decoder \citep{devlin2018bert}.}
\label{fig:fig2}
\end{figure}
The Transformer architecture consists of two main components: an encoder and a decoder.The encoder takes in the input sequence and generates a sequence of hidden representations, which are then passed to the decoder. The decoder then uses the encoder's output to generate the final output sequence.

We will be utilizing Bidirectional Encoder Representations from Transformers (BERT) for our sentiment analysis. BERT is a transformer model developed by Google that can perform multiple Natural Language Processing tasks such as sentiment analysis, text classification, chatbots, text extraction, machine translation, text summarization, market intelligence, auto-correct, intent classification, urgency detection, and speech recognition.

This model was initially trained on Wikipedia and Google’s BooksCorpus which contain 2,500,000,000 words and 800,000,000 words respectively. Training of BERT was completed over a period of 4 days using 64 Tensor Processing Units running in parallel. With this much data, it is able to understand context clues making it a very effective model for the purposes of sentiment analysis.

We will be specifically using distil-BERT which is a version of BERT with 12 transformation layers, and 768 Hidden Layers.\citep{muller_2022} This is more reasonable for the task we have at hand and we will implement this using the Hugging Face transformers pipeline package\citep{huggingface2023}. For each day, the average sentiment score of all tweets was calculated. Sentiment scores range from -1 to 1, where -1 represents a very negative sentiment and 1 represents a very positive sentiment.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\label{sec: results}
\section{Results}

The sentiment analysis took approximately 12 minutes to run and the data generated created 3 new columns in the working dataframe: sentiment, label, and score. Score is a numeric value from the range [0,1] where the higher the score the more confident the sentiment analyzed is correct. This score is the confidence that the model gives for the sentiment assignment and serves as a way to observe sentiment as a continuous variable. When combined and observed as a frequency histogram, it seems that the sentiment scores for the period are centered around a slightly positive value of 0.1 indicating sentiment for the CVX term was generally positive but normally distributed more or less.

\begin{figure}[tbp]
  \begin{center}
  \includegraphics[width=\textwidth]{../figures/fig3.pdf}
  \caption{Sentiment Distribution }\label{fig:fig2}
  \end{center}
\end{figure}

ARMA-GARCH models have several assumptions, including the stationarity of the time series data, the presence of autoregressive and moving average processes, the normality and lack of autocorrelation in the residuals, the constant conditional variance of the data, the absence of autoregressive conditional heteroscedasticity effects, and a sufficient sample size. These assumptions are important to ensure unbiased parameter estimates and accurate predictions. Some of these assumptions such as the normality and lack of autocorrelation in the residuals, the constant conditional variance of the data, the absence of autoregressive conditional heteroscedasticity effects were checked manually by making plots using R as such:

\jy{reference to figures/tables by their labels. Never H or h. Always tbp for floating locations.}
\begin{figure}[!hb]
  \begin{center}
  \includegraphics[width=\textwidth]{../figures/fig4.pdf}
  \caption{Garch Model Residuals}\label{fig:fig1}
  \end{center}
\end{figure}

\jy{a blank line means a new paragraph}

and those that remained were checked by the rugarch\citep{rugarch}, readr\citep{readr}, forecast\citep{forecast}, tseries\citep{tseries}, garchx\citep{garchx}, and TSA\citep{TSA} packages.
\jy{space before citep}

In the analysis, an ARMA-GARCH model was first created only using the daily sentiment and then comparing to an ARMA-GARCH model with daily sentiment as an exogenous variable. The ARMA part of this technique, models the autocorrelation and moving average patterns in the data and GARCH models the volatility or conditional heteroskedasticity of the data. To determine whether daily sentiment, the exogenous variable has any effect on the model, we conducted the Likelihood ratio test. The log likelihood values for the base model and the model with sentiment as a variable are 1293.56 and 504.85, respectively.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\label{sec: discussion}
\section{Discussion}

As mentioned before, this paper is the first one to take the approach of using Transformers to determine whether twitter sentiment is informative in predicting the volatility of the stock price of the Chevron Corporation. In summary, this paper accomplished this task through the following:
\begin{itemize}
    \item Introducing some background behind the Chevron Corporation and Sentiment Analysis as a Practice.
    \item Describing the data and the methods by which the data was obtained.
    \item Describing the methods behind the sentiment analysis and correlation derivation.
    \item Describing the results.
\end{itemize}

\jy{close figure/table captions with a period.}

\jy{no need for paragraph titles}
\paragraph{Possible Expansions}
One possible expansion of this study would be to increase the sample size to include more observations and thus increase the robustness of the analysis. This would allow for more accurate statistical tests and a better understanding of the relationship between sentiment and stock price movement/volatility. Another possible expansion would be to test for causality using techniques like the Granger causality test, which would allow us to determine whether sentiment scores are truly predictive of stock price movements or whether they are just correlated. Additionally, conducting a meta-analysis of multiple companies in the fossil fuel industry or across multiple industries could provide broader insights into the relationship between sentiment and stock prices.

@@

\paragraph{Conclusion}
Overall, this study provides valuable insights into the use of Twitter sentiment analysis as a tool for predicting stock prices, and points towards potential avenues for further research. With further research, determined but analyzing the effect of public sentiment on stock prices of fossil fuel companies can provide valuable insight into how public opinion can be used to augment or reduce the effects of climate change.

\jy{no manually controlled spacing}

\bibliographystyle{chicago}
\bibliography{references}
